### 2020-11-12 Thesis-Chapter5-ThreatModel.tex
Develop more threats

@@

\modelitem{Breakdown in rule of law}{This threat model assumes that the legal process used to obtain the warrant is
valid. Additionally, all forms of surveillance, even when protected from mass surveillance, require oversight.
Transparency via auditability, preferably ensured via technical mechanism, is a goal for good \ac{EA} proposals.
However, rule of law is an absolute prerequisite for which no \ac{EA} mechanism can compensate.}

@@

\begin{table}[h]
  \caption{Central Concepts in the \ldawmsr Proposal}
  \label{table-ldawmsr-concepts}
  \FlushLeft
  \small
  \begin{tabular}{ |l|p{6.3cm}|p{6.3cm}| }
    \hline
    \thead{Concept} & \thead{Implementation} & \thead{Outcome} \\ \hline
    Self-escrow
    & The Class key is escrowed in the device's Secure Enclave (or equivalent) using a write-only component; i.e.,
      software can update the key, but only an unexposed hardware interface can read it.
    & Since the Class key itself is being stored, there is no change to the security of the underlying cryptographic
      protocols. Physical possession and partial disassembly is required, which introduces practical barriers to mass
      surveillance.
    \\ \hline
    Time vaulting
    & The hardware interface responds to requests only after proof of sustained possession for a ``lockup period (e.g.,
      72 hours).''
    & The waiting period precludes ``sneak and peak'' attacks and further reduces the utility for mass surveillance.
    \\ \hline
    Authorization
    & After the lockup period, the requestor must provide evidence of authorization. This comes from a shared secret
      between the device and the manufacturer which can be obtained via legal process.
    & Physical possession is now not enough; law enforcement (or attackers) must provide this secret information to the
      device to unlock it.
    \\ \hline
    Transparency
    & In addition to the device disassembly, the escrow agent modifies the device (e.g., burns a fuse) when it has been
      unlocked. The device firmware detects this modification.
    & The device user has evidence that the device has been unlocked, preventing covert usage.
    \\ \hline
  \end{tabular}
\end{table}

@@

\begin{figure}[h!]
  \centering\CaptionFontSize
  \includegraphics[width=0.9\linewidth]{dfds/build/DAR-level-1-crypto-iphone-LDAMSR-setup.png}
  \caption{The LDAWMSR maintenance data flow diagram.}
  \label{fig-dfd-ldawmsr-setup}
\end{figure}

@@

% Full lifecycle--how do the keys get in the DB!

The proposal has been illustrated. What threats does it introduce? Recall from \mysec{sec-crypto-basics} that security
can be expressed in the properties of authentication, integrity, non-repudiation, confidentiality, availability, and
authorization. Threats are often expressed as the negative of these properties: spoofing, tampering, repudiation,
information disclosure, denial of service, and elevation of privileged \cite{shostack_threat_2014}. This section
analyzes \ldawmsr using these categories.

@@

\newcommand{\threattablebegin}[3]{
  \begin{FlushLeft}
    \small
    \begin{longtable}{ lp{3cm}p{5.6cm}p{5.6cm} }
      \caption{#1 Threats}
      \label{table-#2}
      \\ \toprule
      \thead{ID} & \thead{#3} & \thead{Effect} & \thead{Mitigation}
      \\ \midrule
      \endfirsthead
      \caption[]{#1 Threats (continued)}
      \\
      \toprule
      \thead{ID} & \thead{#3} & \thead{Effect} & \thead{Mitigation}
      \\
      % \midrule
      \endhead
      \endfoot
      \bottomrule
      \endlastfoot
}

@@

\threattablebegin{Tampering}{tampering}{Tamper}
  T1 & Defensive user corrupts DSK, DID, or token
  & LE attempts at perform \ac{EA} will fail due to corrupt data. Requires compromise of the Secure Enclave or advanced
    hardware manipulation tools.
  & Since these values are known at manufacturing time and never change, they can be made read-only. (The symmetric key
    variant of \ldawmsr requires updating the symmetric equivalent of the public DSK, and is therefore more vulnerable
    to this threat.)
  \\ \hline
  T2 & Defensive user destroys the \ac{EA} hardware interface
  & LE attempts at perform \ac{EA} will fail due to damaged hardware.
  & Manufacture the device to require destructive disassembly to access the interface. This increases the cost
    associated with deploying and using the system.
  \\ \hline
  T3 & LE insider tampers with DID before digital signature
  & .
  & .
\threattableend

@@

@@

@@

@@

>>>>

\modelitem{Supply chain attacks}{Protecting device hardware and software supply chains is necessary to prevent
surreptitious, trivially exploitable backdoors. For the purposes of this threat model, device hardware and software are
considered to be as-intended, though they are assumed to contain the standard amount of bugs and side-channels.}

@@

\modelitem{Breakdown in (or absence of) rule of law}{This threat model assumes that the legal process used to obtain the
warrant is valid. Additionally, all forms of surveillance, even when protected from mass surveillance, require
oversight. Transparency via auditability, preferably ensured via technical mechanism, is a goal for good \ac{EA}
proposals. However, rule of law is an absolute prerequisite for which no \ac{EA} mechanism can compensate.}

@@

\begin{table}[h]
  \caption{Central Concepts in the \ldawmsr Proposal}
  \label{table-ldawmsr-concepts}
  \FlushLeft
  \small
  \begin{tabular}{ |l|p{6.4cm}|p{6.4cm}| }
    \hline
    \thead{Concept} & \thead{Implementation} & \thead{Outcome} \\ \hline
    Self-escrow
    & The Class key is escrowed in the device's Secure Enclave (or equivalent) using a write-only component; i.e.,
      software can update the key, but only an unexposed hardware interface can read it.
    & Since the Class key itself is being stored, there is no change to the security of the underlying cryptographic
      protocols. Physical possession and partial disassembly is required, which introduces practical barriers to mass
      surveillance.
    \\ \hline
    Time vaulting
    & The hardware interface responds to requests only after proof of sustained possession for a ``lockup period (e.g.,
      72 hours).''
    & The waiting period precludes ``sneak and peak'' attacks and further reduces the utility for mass surveillance.
    \\ \hline
    Authorization
    & After the lockup period, the requestor must provide evidence of authorization. This comes from a shared secret
      between the device and the manufacturer which can be obtained via legal process.
    & Physical possession is now not enough; law enforcement (or attackers) must provide this secret information to the
      device to unlock it.
    \\ \hline
    Transparency
    & In addition to the device disassembly, the escrow agent modifies the device (e.g., burns a fuse) when it has been
      unlocked. The device firmware detects this modification.
    & The device user has evidence that the device has been unlocked, preventing covert usage.
    \\ \hline
  \end{tabular}
\end{table}

@@

\begin{figure}[p!]
  \centering\CaptionFontSize
  \includegraphics[width=\linewidth]{dfds/build/DAR-level-1-crypto-iphone-LDAMSR-setup.png}
  \caption{The LDAWMSR maintenance data flow diagram.}
  \label{fig-dfd-ldawmsr-setup}
\end{figure}

@@

The proposal has been illustrated. What threats does it introduce? Recall from \mysec{sec-crypto-basics} that security
can be expressed in the properties of authentication, integrity, non-repudiation, confidentiality, availability, and
authorization. Threats are often expressed as the negative of these properties: spoofing, tampering, repudiation,
information disclosure, denial of service, and elevation of privileged \cite{shostack_threat_2014}. This section
analyzes \ldawmsr using these categories. Threats that fit under multiple categories, such as tampering for the effect
of repudiation, are listed only once.

@@

\newcommand{\threattablebegin}[3]{
  \begin{FlushLeft}
    \small
    \begin{longtable}{ lp{3cm}p{5.2cm}p{6cm} }
      \caption{#1 Threats}
      \label{table-#2}
      \\ \toprule
      \thead{ID} & \thead{#3} & \thead{Effect} & \thead{Mitigation}
      \\ \midrule
      \endfirsthead
      \caption[]{#1 Threats (continued)}
      \\
      \toprule
      \thead{ID} & \thead{#3} & \thead{Effect} & \thead{Mitigation}
      \\
      % \midrule
      \endhead
      \endfoot
      \bottomrule
      \endlastfoot
}

@@

\threattablebegin{Tampering}{tampering}{Tamper}
  T1 & Defensive user corrupts DSK, DID, or token
  & LE attempts at perform \ac{EA} will fail due to corrupt data. Requires compromise of the Secure Enclave or advanced
    hardware manipulation tools.
  & Since these values are known at manufacturing time and never change, they can be made read-only. (The symmetric key
    variant of \ldawmsr requires updating the symmetric equivalent of the public DSK, and is therefore more vulnerable
    to this threat.)
  \\ \hline
  T2 & Defensive user destroys the \ac{EA} hardware interface
  & LE attempts at perform \ac{EA} will fail due to damaged hardware.
  & Manufacture the device to require destructive disassembly to access the interface. This increases the cost
    associated with deploying and using the system.
  \\ \hline
  T3 & LE insider tampers with DID before digital signature
  & LEA receives an unauthorized device's unlock artifacts. Can be combined with other attacks to compromise a device.
  & Randomize DID's to make them unguessable, meaning a target device must be in possession in order for the attacker to
    know what DID to use. Input to the vendor's \ac{HSM} could also include data from the legal documents, such as
    device S/N; the \ac{HSM} would hash the value and verify a match before returning the unlock artifacts.
  \\ \hline
  T4 & Attacker tampers with hardware transparency mechanism
  & The device user is unaware that the device was unlocked. Highly implementation dependent, but certainly requires
    advanced hardware manipulation tools.
  & Manufacture the device to require destructive disassembly to access the interface.
\threattableend

@@

Repudiation threats are listed in \mytab{table-repudiation}.

\threattablebegin{Repudiation}{repudiation}{Repudiation}
  R1 & Attacker or authoritarian government repudiates unlock attempt
  & The user is unaware that someone tried to access their device.
  & Manufacture the device to require destructive disassembly to access the interface, or use the same hardware
    transparency mechanism to mark mere access attempts as well.
  \\ \hline
  R2 & Authoritarian government repudiates demanding vendor assistance
  & Governments not respecting the legal framework governing the system can bully the vendor and try to force access
    while maintaining deniability.
  & This is close to being an out of scope threat under the ``rule of law'' exception. However, one could design the
    system to require requests to be recorded on a public ledger. This opens up several new difficulties.
  \\ \hline
  R3 & LEA repudiates having unlocked a device
  & The device is undeniably unlocked, but the LEA claims it was not them, allowing possible violations of civil
    liberties and harming transparency.
  & ...
  \\ \hline
  R4 & Vendor repudiates having responded to an access request
  & The device is undeniably unlocked, but the vendor claims they did not provide the unlock artifacts, allowing the
    vendor to cover up leaks or unsavory policy decisions by suggesting the device was instead hacked. Harms
    transparency.
  & ...
\threattableend

@@

Information disclosure threats are listed in \mytab{table-disclosure}.

\threattablebegin{Information Disclosure}{disclosure}{Information \\ Disclosed}
  I1 & .
  & .
  & .
  \\ \hline
  I2 & .
  & .
  & .
\threattableend

@@

Denial of service threats are listed in \mytab{table-dos}.

\threattablebegin{Denial of Service}{dos}{Service Denied}
  D1 & .
  & .
  & .
  \\ \hline
  D2 & .
  & .
  & .
\threattableend

@@

Elevation of privilege are listed in \mytab{table-privilege}.

\threattablebegin{Elevation of Privilege}{privilege}{Privilege Gained}
  E1 & .
  & .
  & .
  \\ \hline
  E2 & .
  & .
  & .
\threattableend
